Efficient Computation of Extended Sources

### 2022-03-29 repro/papers/GEM22/paper.tex
near final

\subsection{Synthetic models and simulation}
To illustrate the structure described in the preceding section, I
introduce two 2D acoustic models, one spatially homogeneous, the other
highly refractive. The first, homogenous model has $\kappa = 4$
GPa and $\rho = 1$ g/cm$^3$ throughout a rectangular domain of size 8 km ($x$) $\times$ 4 km
($z$). The second, refractive, model is a perturbation of the first by
a low-velocity acoustic lens positioned in the center of the
rectangle. To produce this structure, the density is chosen
homogeneous as in the first model, while the bulk modulus decreases to
from 4 GPa outside the lens to 1.6 GPA in its center, as shown in Figure \ref{fig:bml0}.

@@

\subsection{Creating downgoing fields}
The downgoing condition constrains high-frequency energy of localized
plane wave components, hence could be enforced by dip
filtering. However, a simpler approach is to construct fields that
must be entirely downgoing at the source and receiver surfaces by
virtue of ray geometry.

@@

% time rev

@@

@@

\subsection{Accurate computation of $\Lambda$}
%Figure \ref{fig:preddinvhshh0} shows the pressure source gather
%produced from the pressure data gather in Figure \ref{fig:dsrcphh0} by
%application of the operator on the right-hand side of formula
%\ref{eqn:lamident} to the source surface pressure gather depicted in
%\ref{fig:dsrcphh0}. The homogeneous model is used in all propagations
%implicit in the prescription \ref{eqn:lamident}. The scale is the same
%as for Figures \ref{fig:dinvhshh0} and \ref{fig:dhshh0}. In fact
%Figure \ref{fig:preddinvhshh0} appears to be nearly identical to
%Figure \ref{fig:dinvhshh0}, and both appear to be dip-filtered
%versions of Figure \ref{fig:dhshh0}. The difference plot (Figure
 % \ref{fig:ddiffinvhshh0}), using the same color scale, shows that the
 % similarity is quantitative. The recovered source gather (Figure
 % \ref{fig:preddinvhshh0}) also generates the same acoustic fields as
  %the point source at $z=z_d$: the pressure gather at $z=z_r=1000$ m
%  depth (propagated in the lens model) is shown in Figure \ref{fig:dpredhsrecplh0}, and its
%  difference with the point source gather (Figure \ref{fig:drecplh0})
%  plotted on the same color scale in Figure
%  \ref{fig:ddiffpredhsrecplh0}.

@@

\subsection{Economical computation of $\Lambda$ in ``thin'' subdomain}
Equation \ref{eqn:lamnear} suggests a thin-slab computation of the
$\Lambda$ action, which is both accurate and economical. 
estimates shown in Figure \ref{fig:preddinvhshh0}. This calculations
place a receiver array at $z_s+\Delta z=2900$ m depth, just 100 m above the
source surface at $z_s=3000$ m. For the discretization used to create
the examples shown so far, that is just a 5 gridpoint difference in
depth, as opposed to 100 gridpoints between the source and receiver
depths for examples such as shown in Figure \ref{fig:drecphh0}.

@@

The approximation to $\Lambda_{z_s}^+$ via equation \ref{eqn:lamnear}
for this configuration is evaluated in the same way as before in
Figures \ref{fig:preddnshslh0}, \ref{fig:ddiffnshslh0},
\ref{fig:dprednshsrecplh0}, and \ref{fig:ddiffprednshsrecplh0}. The effect of aperture
limitation is clearly diminished: the second figure in this series
compares the full-aperture pressure source gather (Figure
\ref{fig:dhshh0}) with the 
image of the corresponding pressure gather (Figure \ref{fig:dsrcphh0})
under the approximation to $\Lambda_{z_s}^+$, and the last figures
show that the approximated source gathers accurately predict the
point-source pressure gather at the receiver datum $z_r=1000$ m.

\subsection{Symmetrizing $\Lambda$}

@@

Figure \ref{fig:compnreslh0} shows the same comparison with non-zero
penalty weight, $\alpha=10^{-3}$. The PCG normal residual curve is
almost identical with that in the $\alpha=0$ case, wheras the CG
convergence has slowed down noticeably, being about five times as slow
as the preconditioned algorithm.

@@

\section{Figures}

\plot{recphh0}{width=\textwidth}{Output pressure gather for point source in 
  homogeneous medium, configuration as described in Figure \ref{fig:bml0} and in
  the text.}

\plot{recplh0}{width=\textwidth}{Output pressure gather for point source in 
  refractive (lens) medium, configuration as described in Figure \ref{fig:bml0} and in
  the text.}

\plot{recvzhh0}{width=\textwidth}{Output vertical velocity gather for point source in 
  homogeneous medium, configuration as described in Figure \ref{fig:bml0} and in
  the text.}

\plot{recvzlh0}{width=\textwidth}{Output vertical velocity gather for point source in 
  refractive (lens) medium, configuration as described in Figure \ref{fig:bml0} and in
  the text.}

\plot{drecphh0}{width=\textwidth}{Pressure gather at receiver depth 
  $z_r=1000$ m from field generated by causal solution of acoustic 
  system \ref{eqn:awepm} in the homogeneous model described in the 
  text, with point pressure source (constitutive defect) at $z_d=3500$
  m, $x_d=3500$ m.}

\plot{dfwdphh0}{width=\textwidth}{Pressure gather at receiver depth
  $z_r=1000$ m from field generated by causal solution of acoustic
  system \ref{eqn:awepm} in the homogeneous model described in the
  text, with extended pressure source (constitutive defect)
  on $z=z_s=3000$ m given by $h_s=-2P_sv_z^+=\Lambda^+_{z_s}P_sp^+$,
  where $P_sp^+$ is shown in Figure \ref{fig:dsrcphh0} and $P_sv^+_z$
  in Figure \ref{fig:dsrcvzhh0}. In this simulation, the velocity
  velocity source (vertical load) vanishes: $f_s=0$.}

\plot{daltphh0}{width=\textwidth}{Pressure gather at receiver depth
  $z_r=1000$ m from field generated by causal solution of acoustic
  system \ref{eqn:awepm} in the homogeneous model described in the
  text, with extended velocity source (vertical load) $f_s=-2P_sp^+$
  on $z=z_s=3000$ m, where $P_sp^+$ is shown in Figure
  \ref{fig:dsrcphh0}.  In this simulation, the zero pressure source
  (constitutive defect vanishes: $h_s=0$.}

\plot{drecphh0tr21}{width=\textwidth}{Overplot of traces 21 ($x=2400$) 
  from gathers shown in \ref{fig:drecphh0} (blue), \ref{fig:dfwdphh0}
  (red).}

\plot{daltphh0tr21}{width=\textwidth}{Overplot of traces 21 ($x=2400$) 
  from gathers shown in \ref{fig:drecphh0} (blue), \ref{fig:daltphh0}
  (red).}

\plot{drecphh0tr51}{width=\textwidth}{Overplot of traces 51 ($x=3000$) 
  from gathers shown in \ref{fig:drecphh0} (blue), \ref{fig:dfwdphh0}
  (red).}

\plot{daltphh0tr51}{width=\textwidth}{Overplot of traces 51 ($x=3000$) 
  from gathers shown in \ref{fig:drecphh0} (blue), \ref{fig:daltphh0}
  (red).}

\plot{drecphh0tr81}{width=\textwidth}{Overplot of traces 81 ($x=3600$) 
  from gathers shown in \ref{fig:drecphh0} (blue), \ref{fig:dfwdphh0}
  (red).}

\plot{daltphh0tr81}{width=\textwidth}{Overplot of traces 81 ($x=3600$) 
  from gathers shown in \ref{fig:drecphh0} (blue), \ref{fig:daltphh0}
  (red).}

\plot{drecplh0tr21}{width=\textwidth}{Overplot of traces 21 ($x=2400$) 
  from gathers shown in \ref{fig:drecplh0} (blue), \ref{fig:dfwdplh0}
  (red).}

\plot{daltplh0tr21}{width=\textwidth}{Overplot of traces 21 ($x=2400$) 
  from gathers shown in \ref{fig:drecplh0} (blue), \ref{fig:daltplh0}
  (red).}

\plot{drecplh0tr51}{width=\textwidth}{Overplot of traces 51 ($x=3000$) 
  from gathers shown in \ref{fig:drecplh0} (blue), \ref{fig:dfwdplh0}
  (red).}

\plot{daltplh0tr51}{width=\textwidth}{Overplot of traces 51 ($x=3000$) 
  from gathers shown in \ref{fig:drecplh0} (blue), \ref{fig:daltplh0}
  (red).}

\plot{daltplh0tr81}{width=\textwidth}{Overplot of traces 81 ($x=3600$)
  from gathers shown in \ref{fig:drecplh0} (blue), \ref{fig:daltplh0}
  (red).}

\plot{dinvhshh0}{width=\textwidth}{Approximate inversion via first 
  equation in display \ref{eqn:approxinv}. Inversion in homogenous model of 
  the pressure gather in Figure \ref{fig:drecphh0}, simulated with 
  homogeneous model. Scaled version of output $v_z$ field obtained by 
  applying transpose of $4V^+_{z_s,z_r}$. Approximates dip-filtered
  version of pressure source gather (Figure \ref{fig:dhshh0}).}

\plot{drerecphh0}{width=\textwidth}{Re-simulated pressure gather
  produced from inverted source
  shown in Figure \ref{fig:dinvhshh0}. Simulation in homogeneous model.}

\plot{ddiffrecphh0}{width=\textwidth}{Difference between gathers
  displayed in Figures \ref{fig:drecphh0} and \ref{fig:drerecphh0},
  plotted on same color scale.}

\plot{dinvhsll0}{width=\textwidth}{Approximate inversion via first 
  equation in display \ref{eqn:approxinv}. Inversion in lens model of 
  the pressure gather in Figure \ref{fig:drecplh0}, simulated with 
  lens model. Scaled version of output $v_z$ field obtained by 
  applying transpose of $4V^+_{z_s,z_r}$. Approximates dip-filtered
  version of pressure source gather (Figure \ref{fig:dhshh0}).}

\plot{drerecpll0}{width=\textwidth}{Re-simulated pressure gather
  produced from inverted source
  shown in Figure \ref{fig:dinvhsll0}. Simulation in lens model.}

\plot{ddiffrecpll0}{width=\textwidth}{Difference between gathers
  displayed in Figures \ref{fig:drecpll0} and \ref{fig:drerecpll0},
  plotted on same color scale.}

\plot{drerecplh0}{width=\textwidth}{Re-simulated pressure gather produced from
  inverted source
  shown in Figure \ref{fig:dinvhslh0}. Simulation in lens model.}

\plot{dfwdvzhh0}{width=\textwidth}{Vertical velocity gather, generated
  with a pressure source in the homogeneous model, 
  corresponding to pressure gather \ref{fig:dfwdphh0}.}

\plot{daltvzhh0}{width=\textwidth}{Vertical velocity gather, generated
  with a velocity source in the homogenous model, corresponding to
  pressure gather \ref{fig:daltphh0}.}

\plot{dsvcomphh0}{width=\textwidth}{Difference between velocity gathers
  shown in Figures \ref{fig:dfwdvzhh0} and \ref{fig:daltvzhh0},
  plotted on the same color scale as these figures.}

\plot{lamsstlamrdrecphh0}{width=\textwidth}{Inversion of data shown in
  Figure \ref{fig:drecphh0}, simulated in homogeneous model, using the
  approximate unitarity relation \ref{eqn:unitary} and propagation in
  homogenous model.}

\plot{difflamsstlamrdrecphh0}{width=\textwidth}{Difference between
  data displayed in Figures \ref{fig:dinvhshh0} and
  \ref{fig:lamsstlamrdrecphh0}, plotted on the same color scale.}

\plot{preddinvhshh0}{width=\textwidth}{Pressure source gather = image
  of pressure-to-source operator $\Lambda^+_{z_s}$ applied to pressure gather
  shown in Figure \ref{fig:dsrcphh0}, homogeneous model. Compare Figure
  \ref{fig:dinvhshh0}.}

\plot{ddiffinvhshh0}{width=\textwidth}{Difference between (a) image
  (Figure \ref{fig:preddinvhshh0}) of $\Lambda^+_{z_s}$ applied to
  pressure gather (Figure \ref{fig:dsrcphh0}), and (b) source gather
  (Figure \ref{fig:dinvhshh0}) inverted from receiver pressure gather
  (Figure \ref{fig:drecphh0}). Homogeneous model used in all
  propagations. Same color scale as in Figure
  \ref{fig:preddinvhshh0}. }

\plot{dpredhsrecphh0}{width=\textwidth}{Pressure gather at receiver 
  datum $z=z_r=1000$ m simulated in homogeneous model from source 
  gather shown in Figure \ref{fig:preddinvhshh0}, also based on the 
  homogeneous model. Compare with point source pressure gather (Figure 
  \ref{fig:drecphh0}).}

\clearpage

\plot{ddiffpredhsrecphh0}{width=\textwidth}{Plot of difference 
  between data shown in Figures \ref{fig:drecphh0} and 
  \ref{fig:dpredhsrecphh0}, plotted on same color scale as the latter 
  two figures.}

\plot{preddinvhsll0}{width=\textwidth}{Pressure source gather = image
  of pressure-to-source operator $\Lambda^+_{z_s}$ applied to pressure gather
  shown in Figure \ref{fig:dsrcphh0}, lens model. Compare Figure
  \ref{fig:dinvhsll0}.}

\plot{ddiffinvhsll0}{width=\textwidth}{Difference between (a) image
  (Figure \ref{fig:preddinvhsll0}) of $\Lambda^+_{z_s}$ applied to
  pressure gather (Figure \ref{fig:dsrcphh0}), and (b) source gather
  (Figure \ref{fig:dinvhsll0}) inverted from receiver pressure gather
  (Figure \ref{fig:drecplh0}). Lens model used in all propagations.
  Same color scale as in Figure \ref{fig:preddinvhsll0}.}

\plot{dpredhsrecpll0}{width=\textwidth}{Pressure gather at receiver 
  datum $z=z_r=1000$ m simulated in lens model from source 
  gather shown in Figure \ref{fig:preddinvhsll0}, also based on the 
  homogeneous model. Compare with point source pressure gather (Figure 
  \ref{fig:drecplh0}).}

\plot{ddiffpredhsrecpll0}{width=\textwidth}{Plot of difference 
  between data shown in Figures \ref{fig:drecplh0} and 
  \ref{fig:dpredhsrecpll0}, plotted on same color scale as the latter 
  two figures.}

\clearpage

\plot{ddiffnshshh0}{width=\textwidth}{Difference between (a) image
  (Figure \ref{fig:preddnshshh0}) of $\Lambda^+_{z_s}$ applied to
  pressure gather (Figure \ref{fig:dsrcphh0}) using a near receiver
  array to implement formula \ref{eqn:lamident}, and (b) source gather
1650  (Figure \ref{fig:dhshh0}) inferred from vertical velocity.
  Homogeneous model used in all
  propagations. Same color scale as in Figure
  \ref{fig:preddnshshh0}. }

\plot{dprednshsrecphh0}{width=\textwidth}{Pressure gather at receiver
  datum $z=z_r=1000$ m simulated from source gather shown in Figure
  \ref{fig:preddnshshh0}. Compare with point source pressure gather
  (Figure \ref{fig:drecplh0}).}

\clearpage

\plot{ddiffprednshsrecphh0}{width=\textwidth}{Plot of difference 
  between data shown in Figures \ref{fig:drecphh0} and 
  \ref{fig:dpredhsrecphh0}, plotted on same color scale as the latter 
  two figures.}

\plot{compres0hh0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  homogeneous model, point source (Figure \ref{fig:recphh0}), inversion 
  in homogeneous model. Penalty weight
  $\alpha=0$.}

\plot{compres0lh0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  lens model, point source (Figure \ref{fig:recplh0}), inversion 
  in homogenous model. Penalty weight 
  $\alpha=0$.}

\plot{compres0ll0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  lens model, point source (Figure \ref{fig:recplh0}), inversion 
  in lens model. Penalty weight 
  $\alpha=0$.}

\plot{compres1hh0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  homogeneous model, point source (Figure \ref{fig:recphh0}), inversion 
  in homogenous model. Penalty weight 
  $\alpha=10^{-3}$.}

\plot{compres1lh0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  lens model, point source (Figure \ref{fig:recplh0}), inversion 
  in homogenous model. Penalty weight 
  $\alpha=10^{-3}$.}

\plot{compres1ll0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  lens model, point source (Figure \ref{fig:recplh0}), inversion 
  in lens model. Penalty weight
  $\alpha=0$.}

\plot{compnres0hh0}{width=\textwidth}{Comparison of normal residual
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted
  vs. iteration. Data = homogeneous model, point source (Figure
  \ref{fig:recphh0}), inversion in homogenous model. Penalty weight $\alpha=0$.}

\plot{compnres0ll0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in lens model. Penalty weight 
  $\alpha=0$.}

\plot{compnres1hh0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = homogeneous model, point source (Figure 
  \ref{fig:recphh0}), inversion in homogenous model. Penalty weight 
  $\alpha=10^{-3}$.}

\plot{compnres1ll0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in lens model. Penalty weight
  $\alpha=10^{-3}$.}

\newpage

>>>>

\subsection{Synthetic models and simulation}
To illustrate the structure described in the preceding section, I
introduce two 2D acoustic models, one spatially homogeneous, the other
highly refractive. The first, homogenous model has $\kappa = 4$
GPa and $\rho = 1$ g/cm$^3$ throughout a rectangular domain of size 8 km ($x$) $\times$ 4 km
($z$). The second, refractive, model is a perturbation of the first by
a low-velocity acoustic lens positioned in the center of the
rectangle (Figure \ref{fig:bml0}. To produce this structure, the density is chosen
homogeneous as in the first model, while the bulk modulus decreases to
from 4 GPa outside the lens to 1.6 GPA in its center, as shown in Figure \ref{fig:bml0}.

@@

\subsection{Creating downgoing fields}
The downgoing condition constrains high-frequency energy of localized
plane wave components, hence could be enforced by dip>
filtering. However, a simpler approach is to construct fields that
must be entirely downgoing at the source and receiver surfaces by
virtue of ray geometry.

@@

\plot{daltplh0tr81}{width=\textwidth}{Overplot of traces 81 ($x=3600$)
  from gathers shown in \ref{fig:drecplh0} (blue), \ref{fig:daltplh0}
  (red).}
% time rev

@@

\plot{drerecplh0}{width=\textwidth}{Re-simulated pressure gather produced from
  inverted source
  shown in Figure \ref{fig:dinvhslh0}. Simulation in homogenous model
  used for inversion.}

@@

\plot{dfwdvzlh0}{width=\textwidth}{Vertical velocity gather, generated
  with a pressure source in the lens model, 
  corresponding to pressure gather \ref{fig:dfwdplh0}.}

\plot{daltvzlh0}{width=\textwidth}{Vertical velocity gather, generated
  with a velocity source in the lens model, corresponding to
  pressure gather \ref{fig:daltphh0}.}

\plot{dsvcomplh0}{width=\textwidth}{Difference between velocity gathers
  shown in Figures \ref{fig:dfwdvzhh0} and \ref{fig:daltvzhh0},
  plotted on the same color scale as these figures.}

%Figure \ref{fig:preddinvhshh0} shows the pressure source gather
%produced from the pressure data gather in Figure \ref{fig:dsrcphh0} by
%application of the operator on the right-hand side of formula
%\ref{eqn:lamident} to the source surface pressure gather depicted in
%\ref{fig:dsrcphh0}. The homogeneous model is used in all propagations
%implicit in the prescription \ref{eqn:lamident}. The scale is the same
%as for Figures \ref{fig:dinvhshh0} and \ref{fig:dhshh0}. In fact
%Figure \ref{fig:preddinvhshh0} appears to be nearly identical to
%Figure \ref{fig:dinvhshh0}, and both appear to be dip-filtered
%versions of Figure \ref{fig:dhshh0}. The difference plot (Figure
 % \ref{fig:ddiffinvhshh0}), using the same color scale, shows that the
 % similarity is quantitative. The recovered source gather (Figure
 % \ref{fig:preddinvhshh0}) also generates the same acoustic fields as
  %the point source at $z=z_d$: the pressure gather at $z=z_r=1000$ m
%  depth (propagated in the lens model) is shown in Figure \ref{fig:dpredhsrecplh0}, and its
%  difference with the point source gather (Figure \ref{fig:drecplh0})
%  plotted on the same color scale in Figure
%  \ref{fig:ddiffpredhsrecplh0}.

@@

\subsection{Economical computation of $\Lambda$ in ``thin'' subdomain}
Equation \ref{eqn:lamnear} suggests a thin-slab computation of the
$\Lambda$ action, which is both accurate and economical. 
This calculations
place a receiver array at $z_s+\Delta z=2900$ m depth, just 100 m above the
source surface at $z_s=3000$ m. For the discretization used to create
the examples shown so far, that is just a 5 gridpoint difference in
depth, as opposed to 100 gridpoints between the source and receiver
depths for examples such as shown in Figure \ref{fig:drecplh0}.

@@

The approximation to $\Lambda_{z_s}^+$ via equation \ref{eqn:lamnear}
for this configuration is evaluated in
Figures \ref{fig:preddnshshh0}, \ref{fig:ddiffnshshh0},
\ref{fig:dprednshsrecplh0}, and \ref{fig:ddiffprednshsrecplh0}. The effect of aperture
limitation is clearly diminished: the second figure in this series
compares the full-aperture pressure source gather (Figure
\ref{fig:dhshh0}) with the 
image of the corresponding pressure gather (Figure \ref{fig:dsrcphh0})
under the approximation to $\Lambda_{z_s}^+$, and the last figures
show that the approximated source gathers accurately predict the
point-source pressure gather at the receiver datum $z_r=1000$ m.

\plot{ddiffnshshh0}{width=\textwidth}{Difference between (a) image
  (Figure \ref{fig:preddnshshh0}) of $\Lambda^+_{z_s}$ applied to
  pressure gather (Figure \ref{fig:dsrcphh0}) using a near receiver
  array to implement formula \ref{eqn:lamident}, and (b) source gather
  (Figure \ref{fig:dhshh0}) inferred from vertical velocity.
  Homogeneous model used in all
  propagations. Same color scale as in Figure
  \ref{fig:preddnshshh0}. }

%\plot{dprednshsrecplh0}{width=\textwidth}{Pressure gather at receiver
%  datum $z=z_r=1000$ m simulated in lens model from source gather shown in Figure
%  \ref{fig:preddnshshh0}. Compare with point source pressure gather
%  (Figure \ref{fig:drecplh0}).}

%\plot{ddiffprednshsrecplh0}{width=\textwidth}{Plot of difference 
%  between data shown in Figures \ref{fig:drecplh0} and 
%  \ref{fig:dprednshsrecplh0}, plotted on same color scale as the latter 
% two figures.}

\plot{dprednshsrecpll0}{width=\textwidth}{Pressure gather at receiver
  datum $z=z_r=1000$ m simulated in lens model from source gather shown in Figure
  \ref{fig:preddnshshh0}. Compare with point source pressure gather
  (Figure \ref{fig:drecplh0}).}

\plot{ddiffprednshsrecpll0}{width=\textwidth}{Plot of difference 
  between data shown in Figures \ref{fig:drecplh0} and 
  \ref{fig:dprednshsrecplh0}, plotted on same color scale as the latter 
  two figures.}
\subsection{Symmetrizing $\Lambda$}

@@

Figure \ref{fig:compnres1lh0} shows the same comparison with non-zero
penalty weight, $\alpha=10^{-3}$. The PCG normal residual curve is
almost identical with that in the $\alpha=0$ case, wheras the CG
convergence has slowed down noticeably, being about five times as slow
as the preconditioned algorithm.

@@
